Adding selection to \stdpopsim: oh how the tables have turned

### 2024-12-09 analysis2_manuscript.tex
minor fix

\section*{Detection of Selective Sweeps}
    \label{sweeps}
    We next highlight how the new models of selection in \stdpopsim can be used to benchmark and compare the performance of different methods for detecting selective sweeps from genetic data.
    Here, we performed simulations of human chromosome 1 under the three population out-of-Africa model from \cite{gutenkunst2009inferring} with purifying selection acting on exons under the gamma-distributed DFE described above, the HapMap II genetic map \citep{international2007second}, but also include sweeps.
    In particular, we introduced a beneficial mutation at a given location (to be varied) in the genome at a given time, and with a moderately strong selection coefficient ($s = 0.03$; $2Ns \sim 600$).
    For each sweep location, we performed 2000 replicate simulations, sampling from them only if the selected allele reached a frequency of 0.95 or greater.
    Rather than simulate the entire chromosome arm, replicate simulations were performed on 5cM regions of the chromosome at each of 100 different locations.
    As recombination rate varies across the genome, the size of the region in base pairs simulated varies, however the recombination distance, which is critical for the linked effects of a sweep, is held constant.

>>>>

\section*{Detection of Selective Sweeps}
    \label{sweeps}
    We next highlight how the new models of selection in \stdpopsim can be used to benchmark and compare the performance of different methods for detecting selective sweeps from genetic data.
    Here, we performed simulations of human chromosome 1 under the three population out-of-Africa model from \cite{gutenkunst2009inferring} with purifying selection acting on exons under the gamma-distributed DFE described above, the HapMap II genetic map \citep{international2007second}, but also include sweeps.
    In particular, we introduced a beneficial mutation at a given location (to be varied) in the genome at a given time, and with a moderately strong selection coefficient ($s = 0.03$; $2Ns \sim 600$).
    For each sweep location, we performed 1000 replicate simulations, sampling from them only if the selected allele reached a frequency of 0.95 or greater.
    Rather than simulate the entire chromosome arm, replicate simulations were performed on 5cM regions of the chromosome at each of 100 different locations.
    As recombination rate varies across the genome, the size of the region in base pairs simulated varies, however the recombination distance, which is critical for the linked effects of a sweep, is held constant.
